Local Type Inference for Polarised System F with Existentials

### 2023-10-05 oopsla24/paper.tex
Restructure
WIP

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  A clear and well-documented \LaTeX\ document is presented as an
  article formatted for publication by ACM in a conference proceedings
  or journal publication. Based on the ``acmart'' document class, this
  article presents and explains many of the common variations, as well
  as many of the formatting elements an author may use in the
  preparation of the documentation of their work.
\end{abstract}

@@

$[[iN = iM]]$

\input{tex/01-introduction.tex}

\section{Overview}
\input{tex/02-overview.tex}

\section{Declarative System}
\input{tex/03-declarative-system.tex}

\section{Algorithm}
\input{tex/04-algorithm.tex}

\section{Proof}
\input{tex/05-proof.tex}

\section{Extensions}
\input{tex/06-extensions.tex}

\section{Conclusion}
\input{tex/07-conclusion.tex}

@@

\printbibliography

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  {\color{red}CHANGE!!}
  This paper addresses the challenging problem of type inference for
  Impredicative System F with existential types, a critical aspect of many
  programming languages. While System F serves as the basis for type systems in
  numerous languages, existing type inference techniques for Impredicative
  System F are undecidable due to the presence of existential ($[[∃]]$) 
  and polymorphic ($[[∀]]$) types. Consequently, current algorithms are often ad-hoc and
  sub-optimal. This paper presents novel contributions in the form of a local
  type inference algorithm for Impredicative System F with existential types.
  The algorithm introduces innovative techniques, such as a unique combination
  of unification and anti-unification, a full correctness proof, and the use of
  control structures inspired by \CBPV. Additionally, the paper discusses a type
  inference framework that allows the algorithm to be applied to different type
  systems, offering insights into the under-researched area of impredicative
  existential type inference. 
\end{abstract}

@@

\input{\genDir/tex/01-introduction.tex}

\section{Overview}
\input{\genDir/tex/02-overview.tex}

\section{Declarative System}
\input{\genDir/tex/03-declarative-system.tex}

\section{Algorithm}
\input{\genDir/tex/04-algorithm.tex}

\section{Proof}
\input{\genDir/tex/05-proof.tex}

\section{Extensions}
\input{\genDir/tex/06-extensions.tex}

\section{Conclusion}
\input{\genDir/tex/07-conclusion.tex}

@@

%% Bibliography
%% \balance %% necessary for two-column formats
\printbibliography

\lstset{basicstyle=\ttfamily\scriptsize,keywordstyle=\color{black}\bfseries\underbar,tabsize=8,showstringspaces=false,frame=L,label= ,caption= ,captionpos=b,numbers=none}

\clearpage
\appendix
% \input{./tex/appendix/recovery.tex}
% \input{./tex/appendix/drf.tex}
